---
title: "Homework 6"
author: "Hongjie Liu"
output: github_document
---


Load necessary packages for homework 6.

```{r loadpackages, message = FALSE}
library(tidyverse)
```


## Problem 1

Load the dataset.

```{r p1_load, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Problem 2

Load the dataset. Create a `city_state` variable and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. We limit our analysis those for whom `victim_race` is `white` or `black`.

```{r p2_readtidy, message = FALSE}
homicide_df =
  read_csv("./data/homicide-data.csv") %>% 
  unite(city_state, city:state, sep = ", ") %>% 
  filter(
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black")
  ) %>% 
  mutate(victim_age = as.numeric(victim_age))
```

