---
title: "Homework 6"
author: "Hongjie Liu"
output: github_document
---


Load necessary packages for homework 6.

```{r loadpackages, message = FALSE}
library(tidyverse)
```


## Problem 1

Load the dataset.

```{r p1_load, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Problem 2

Load the dataset. We create a `city_state` variable and a binary variable indicating whether the homicide is solved. We omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. We also omit Tulsa, AL – this is a data entry mistake. We limit our analysis those for whom `victim_race` is `white` or `black`.

```{r p2_readtidy, message = FALSE}
homicide_df =
  read_csv("./data/homicide-data.csv") %>% 
  unite(city_state, city:state, sep = ", ") %>% 
  filter(
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black")
  ) %>% 
  mutate(
    solved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), FALSE, TRUE),
    victim_age = as.numeric(victim_age),
    victim_sex = ifelse(victim_sex == "Unknown", NA, victim_sex),
    victim_sex = as.factor(victim_sex),
    victim_race = as.factor(victim_race)
  )
```

For the city of Baltimore, MD, we use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. We save the output of `glm` as an R object; apply the `broom::tidy` to this object; and obtain the estimate and 95% confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r p2_regression}
baltimore_fit =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = .)

baltimore_fit %>% 
  broom::tidy() %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    aor_estimate = exp(estimate),
    aor_low = exp(estimate - qnorm(.975) * std.error),
    aor_high = exp(estimate + qnorm(.975) * std.error)
  ) %>% 
  select(aor_estimate, aor_low, aor_high) %>% 
  knitr::kable(
    col.names = c("Estimate", "Lower bound of the 95% CI", "Upper bound of the 95% CI"),
    digits = 3
  )
```

